Programming Language Survey Paper on Haskell

### 2013-04-21 projects/term_paper/paper.tex
Added appendix to paper and moved Haskell files for project to src/ for relative import.
Added more iteration examples.

\usepackage{minted}

@@

\subsection{Control Abstractions}
\subsubsection{Expressions}
\bi
    \item Function definitions
\begin{minted}{haskell}
greet :: String -> String
greet name = "Hello, " ++ name ++ "!"
\end{minted}
    \item Bindings: let/in (valid expression), where (locally bound to a syntactic construct)
\begin{minted}{haskell}
rectPrismVol :: (Num a) -> a -> a -> a -> a
rectPrismVol length width height = 4 * (faceArea length width)
    + 2 * (baseArea length height)
where   faceArea l w = l * w
        baseArea = l * h
\end{minted}
\begin{minted}{haskell}
myExp =
    let e = 2.7182
    in  e ** x
\end{minted}
NOTE: statements in let/in must be aligned in same column
\ei

@@

\subsubsection{Iterative Constructs}
\bi
    \item List comprehensions
\begin{minted}{haskell}
filterModThree :: [Int] -> [Int]
filterModThree xs = [x | x <- xs, x `mod` 3 == 0]
\end{minted}
    \item Map/fold
    \item Recursion
\ei

@@

\bibliographystyle{abbrv}
\bibliography{paper}

>>>>

\usepackage{appendix}
\usepackage{minted}

@@

\subsection{Control Abstractions}
\subsubsection{Expressions}
\bi
    \item Function definitions
\begin{minted}{haskell}
greet :: String -> String
greet name = "Hello, " ++ name ++ "!"
\end{minted}
    \item Bindings: let/in (valid expression), where (locally bound to a syntactic construct)
\begin{minted}{haskell}
rectPrismVol :: (Num a) -> a -> a -> a -> a
rectPrismVol length width height = 4 * (faceArea length width)
    + 2 * (baseArea length height)
where   faceArea l w = l * w
        baseArea = l * h
\end{minted}
\begin{minted}{haskell}
myExp :: Float -> Float
myExp x =
    let e = 2.7182
    in  e ** x
\end{minted}
NOTE: statements in let/in must be aligned in same column
\ei

@@

\subsubsection{Iterative Constructs}
\bi
    \item List comprehensions
\begin{minted}{haskell}
filterModThree :: [Int] -> [Int]
filterModThree xs = [x | x <- xs, x `mod` 3 == 0]
\end{minted}
    \item Map/fold
\begin{minted}{haskell}
sumSquares :: (Num a) => [a] -> a
sumSquares xs = foldr1 (+) (map (**2) xs)
\end{minted}
    \item Recursion
\begin{minted}{haskell}
countdown :: Int -> String
countdown 0 = "Blast-off!"
countdown x = (show x) ++ "...\n" ++ countdown (x-1)
\end{minted}
\ei

@@

\newpage
\begin{appendices}
\section{Project Implementation in Haskell}
\inputminted{haskell}{src/InfixPostfix.hs}
\newpage
\inputminted{haskell}{src/InfixPostfixTest.hs}
\end{appendices}

\newpage
\bibliographystyle{abbrv}
\bibliography{paper}
